\documentclass{letter}
%\usepackage[inner=2.5cm,outer=3cm,bottom=2cm,top=2cm]{geometry}
\setlength\topmargin{-2cm}
\setlength\textheight{10in}
\usepackage{hyperref}
\signature{Jeremy Wright}
\address{Jeremy Wright\\jlwrigh1@asu.edu}
\begin{document}
\begin{letter}{}
\opening{Dear ASU 4+1 Admissions Committee:}

I had the opportunity of working with Ryan Dougherty as a student in my CSE~-~394
C++ Programming Practicum course Fall 2013. I feel Ryan exemplifies
two virtues essential for a graduate student: integrity, and an
insatiable passion for learning. 

As an instructor, a graduate student, and full-time software engineer, I am
understand the importance of integrity. Integrity is the linchpin on which
relationships build, academic, and professional alike. As a student in CSE 394, Ryan
approached each project as his own, and excelled in doing so. However, Ryan's
integrity extends beyond his work. Ryan is honest with himself. Ryan is the
first to admit he doesn't know or doesn't understand something. 

As an educator yourself, you understand if one student doesn't
understand something, likely more students confused as well. In class,
I depend on Ryan's frank questions to evaluate the class' understanding as
a whole. Ryan asks clear, concise questions which raises the quality of
everyone's understanding, including my own. Within a graduate environment,
Ryan's ability to discern his own understanding, and prompt questions will not
only further his own success, but those of his class mates
and his instructors. Ryan will have a profound positive effect on his graduate
endeavours. 

Research is what defines a graduate program. Student quality is
essential in providing remarkable papers, and publications to further the
university. Ryan, is unique among his peers. Ryan doesn't approach assignments,
and projects as their weighed impact on his grade. Ryan approaches each as an
opportunity to further his understanding of the world. Within CSE394, the
assignment schedule is set, and self-paced. Ryan finished the required
assignments nearly a month early, and asked for extra projects. Fascinated by
C++ and the concepts he was learning, Ryan was eager to apply these concepts to
a larger project. I am elated to see the results of his passion. 

As a graduate student, Ryan will not be satisfied with the status quo. He will
approach new research with a fresh perspective, and honestly evaluate his own
understanding to deeply investigate new topics. Ryan will systematically address
each frontier with comprehensive attention. Ryan is exactly the type of student
I want in the classes I teach, and the student I want in the research groups
I participate. Thank you for your time. I look forward to seeing the impact Ryan
will make with a Master's Degree.  



\closing{Sincerely,}
\end{letter}
\end{document}
